WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2019-03-02 review/referee_response_0.txt

The authors present a number of new and high-quality transit observations of
the hot Jupiter WASP-4b observed by TESS. After comparing the predicted
mid-transit times (obtained only considering the pre-existing transits in the
literature) with the measured values from the TESS light curves, the authors
conclude that the TESS transits occur ~ 82 seconds earlier than predicted. They
examine different possibilities and find that the 2 most favored scenarios to
explain this deviation are orbital decay and apsidal precession. However, the
authors caution that more observations are needed to confirm these results.
Also, they redetermine various parameters of the system, finding them in
general agreement with literature values.

In general, the manuscript is scientifically accurate and the results presented
in it certainly will be of interest to other investigators in the field. Then,
I consider this paper worthy of being published after the concerns described
below be addressed.

Below are my comments, beginning with the major points. I recommend the authors
take them into consideration when revising their manuscript.

  > RESPONSE: We thank the referee for this summary. In our revision, we
  > have added weight to a third possible explanation that we previously
  > mentioned but did not sufficiently emphasize: a massive outer
  > companion, perhaps on an eccentric orbit, might be able to explain
  > both the transit and radial velocity observations. We have
  > emphasized this possibility throughout the text where appropriate.
  > We have opted against developing a joint model (transits+RVs) for
  > the putative 3-body system, because the RV data show only a weak
  > linear trend. Detection of a periastron passage or any curvature in
  > the radial velocities would be needed for this scenario to be truly
  > convincing.  Instead, we added our own re-analysis of the RV data
  > (now section 4.3, and figure 6) which confirms the Knutson et al
  > (2014) result that the star's acceleration towards our line of sight
  > is only weakly detected, and is an order of magnitude too small to
  > explain the observed period derivative from the transit times.

REFEREE COMMENT:

Major points:

1) In section 3.1, the authors claim "..We included data from peer-reviewed
literature for which the analysis was based on observations of a single,
complete transit,..". However, the transits listed in Table 2 corresponding to
the epochs E=-827 (ttra= 2454697.79817; Winn et al. 2009), E=-804 (ttra=
2454728.57767; Hoyer et al. 2013), E=-537 (ttra= 2455085.88418; Dragomir et al.
2011), E=-208 (ttra= 2455526.16356; Ranjan et al. 2014) are incomplete light
curves, and those from the epochs E=-795 (2454740.62125; Hoyer et al. 2013),
E=-251 (2455468.61943; Hoyer et al. 2013) and E=21 (2455832.61815; Hoyer et al.
2013) present scarcity of after ingress/before egress data-points. On one hand,
given that several partial light curves have been included in their study, the
use of the word "complete" to indicate the characteristics of the transits in
their sample, must be avoided.

On the other hand, at least two other transits included in their sample show
visible anomalies, probably produced by the pass of the planet in front of one
or several cold spots during transit (E=-561, ttra=2455053.76774 and E=-526,
ttra=2455100.60595, both from Sanchis-Ojeda et al. 2011). Different studies
have proven that mid transit-times measured from partial light curves (Sada et
al. 2012, Barros et al. 2013, Nikolov et al. 2015, Mancini et al. 2018) or
light curves with anomalies due to the presence of spots (Oshagh et al. 2013,
Mazeh et al. 2015, Ioannidis et al. 2016), usually present larger uncertainties
and untrustable values. Taking in consideration the conclusions of these
previous works, it is possible that the exclusion of incomplete/with anomalies
transits might affect the outcome of their analysis and conclusions,
particularly with respect to orbital decay and apsidal precession. Then, in
order to warrant confident results, I would like to see the same analysis but
without including partial transits or with visible spot-crossing events on
them.

  > RESPONSE: We thank the referee for this suggestion.  We have removed
  > the word "complete" when describing the transit timing dataset.  We
  > have performed the check requested: We repeated the analysis, but
  > omitting epochs -827, -804, -537, and -208 because of gaps in their
  > coverage.  We also omitted epochs -526 and -561 because of the
  > visible spot anomalies during the transits.
  > 
  > The resulting best-fit transit timing model parameters were all
  > within $1\sigma$ of the values quoted in Table 4.  The confidence
  > intervals, goodness-of-fit statistics $\chi^2$, and model comparison
  > statistics $(AIC, BIC)$ did not appreciably change. 
  > 
  > The most important of these statistics are summarized below for the
  > referee's inspection, and this exercise is described in the new
  > subsection "Systematic Concerns" at the end of Section 3.
  > 
  > ORIGINAL NUMBERS:
  > ##########################################
  > 
  > quadratic model:
  > dP/dt = -4.001e-10 +(3.748e-11) -(3.812e-11)
  > dP/dt = -12.62 +(1.18) -(1.20) millisec/yr
  > 
  > -----chi2 values for best fit parameters-----
  > 
  > linear model:	    chi2: 174.446	dof: 61	AIC: 1.78e+02	BIC: 1.83e+02
  > quadratic model:	chi2: 62.5811	dof: 60	AIC: 6.86e+01	BIC: 7.50e+01
  > precession model: chi2: 64.329	dof: 58	AIC: 7.43e+01	BIC: 8.50e+01
  > 
  > -----quad vs precession-----
  > delta_AIC = AIC_prec-AIC_quad = 5.75
  > delta_BIC = BIC_prec-BIC_quad = 10.03
  > approx Bayes Factor = exp(deltaBIC/2) = 1.14e+04
  > 
  > 
  > NUMBERS WHEN OMITTING PARTIAL TRANSITS AND OBVIOUS SPOT CROSSINGS:
  > ##########################################
  > 
  > quadratic model:
  > dP/dt = -4.098e-10 +(3.909e-11) -(3.862e-11)
  > dP/dt = -12.93 +(1.23) -(1.22) millisec/yr
  > 
  > -----chi2 values for best fit parameters-----
  > 
  > linear model:	     chi2: 163.285	dof: 55	AIC: 1.67e+02	BIC: 1.71e+02
  > quadratic model:	 chi2: 53.5164	dof: 54	AIC: 5.95e+01	BIC: 6.56e+01
  > precession model:  chi2: 56.4648	dof: 52	AIC: 6.65e+01	BIC: 7.67e+01
  > 
  > -----quad vs precession-----
  > delta_AIC = AIC_prec-AIC_quad = 6.95
  > delta_BIC = BIC_prec-BIC_quad = 11.03
  > approx Bayes Factor = exp(deltaBIC/2) = 3.10e+04

REFEREE COMMENT

@@

REFEREE COMMENT

2) As mentioned in 1), another possible interpretation for explaining the
deviation from a linear ephemeris of the TESS mid-transit times could be the
presence of anomalies in the light curves due to stellar activity. It has been
well established that WASP-4 is an active star with a rotation period (P) in
between 20-40 days (P ~ 22 days and P ~ 34 days were determined by
Sanchis-Ojeda et al. 2011 and Hoyer et al. 2013, respectively), which is
expected for a main-sequence G7 star. Given that the TESS mid-transits span
around 30 days, wouldn't it be possible that these measurements be affected by
the existence of unseen stellar spots? Regarding this point, I would like to
see an extra paragraph in the Section "Interpretation" with a discussion about
this scenario.

  > RESPONSE: We have considered this possibility, and have now added
  > the following text in Section 3.3:

  > To explore the effect of possible spot-crossing events on the TESS
  > transit time measurements, we performed a separate test.  We injected
  > triangular spot-anomalies with amplitude $0.03\%$ and duration 30
  > minutes at random phases into each transit.  The amplitudes were
  > larger than the spot-crossing anomalies observed by
  > \citet{southworth_high-precision_2009} and
  > \citet{sanchis-ojeda_starspots_2011}, and the durations were
  > comparable.  Spots of these amplitudes resemble the anomalies present
  > in transits ``1360.54'' and ``1372.58'' of Figure
  > \ref{fig:lightcurves}: they are visible, but at low confidence.
  > 
  > With spots injected, we repeated our measurement of the transit times.
  > On average, the measured transit times did not change with spots
  > injected, because the flux deviations are symmetric about the transit
  > minimum.  For individual transits, there were no cases for which the
  > timing deviation was larger than one minute.  The most concerning
  > shift occurs when the spot anomaly occurs during transit ingress, in
  > which case the measured mid-time is shifted late by between 30 and 50
  > seconds \citep[qualitatively similar to results found
  > by][]{ioannidis_how_2016}.
  > 
  > Therefore the TESS observations could hypothetically all be skewed
  > late if there were spot-crossing events during every ingress.  Two
  > arguments rule out this possibility.  (1) The lightcurve residuals do
  > not show evidence for these events.  (2) The stellar rotation period
  > is between 20 and 40 days, and the sky-projected stellar obliquity is
  > less than 10 degrees
  > \citep{triaud_spin-orbit_2010,sanchis-ojeda_starspots_2011,hoyer_tramos_2013}.
  > Since the planet orbits every 1.3 days, requiring that spot anomalies
  > always occur during ingress would be equivalent to requiring a stellar
  > spot distribution that is exquisitely selected to match the planet
  > ingress times.  Such a spot distribution is rather implausible.

REFEREE COMMENT

@@

-- Minor points:

0. TITLE:

i) As it is, the title implies a very strong asseveration. It would be more
appropriate "Possible Early Arrival of WASP-4b for the TESS Mission" or
something similar.

  > RESPONSE: The main result of the paper is that TESS saw WASP-4b
  > transit 81.6 +/- 11.7 seconds early (~= 7 sigma). Given the
  > statistical significance, we would prefer to keep the title as-is.

REFEREE COMMENT

@@

  > RESPONSE: Done.

REFEREE COMMENT

iii) For the casual reader, it would be important to briefly specify what
"Threshold Crossing Events" means, and what the flags "Reaction Wheel
Desaturation Event" and "Manual Exclude" represent. Footnotes including this
information would be appropriate. Also, could the authors describe what a
"Presearch Data Conditioning" lightcurve is?

  > RESPONSE: We have clarified that a "Presearch Data Conditioning"
  > lightcurve is at a stage of process in which systematic trends
  > have been removed through the decorrelation process described by
  > Smith et al (2017).
  >
  > We now omit explicit mention of "Treshold Crossing Events" in
  > favor of a more qualitative description.
  >
  > As described in the text, the flags "Reaction Wheel Desaturation
  > Event" and "Manual Exclude" together mean that the data are
  > potentially of poor quality due to "momentum dumps".  We referred
  > the reader to the data release notes for an explanation of what a
  > "momentum dump" is, and have added text to this footnote to
  > improve its clarity.

REFEREE COMMENT

@@

  > RESPONSE: We have clarified that the phase-folded lightcurve
  > comes from 18 transits.  We have left the figure ordering
  > as-is.

REFEREE COMMENT

ii) The authors say that the phase-folded lightcurve was fitted by using the
implementation of Kreidberg (2015) of the analytic model of Mandel & Agol
(2002). Is this referring to the BATMAN code? If it is so, It would be good to
mention the code's name in the text. Also, I would appreciate if, in the main
text, the authors clarify from which source are the values used as initial
photometric parameters (planet to star radius ratio, orbital distance to
stellar radius ratio, inclination, etc). On the other hand, for highlighting
the results obtained with TESS data, it would be important to visualize all the
transit parameters derived from section 2.2 in an independent table.
Furthermore, to see the agreement between the transit parameters reported in
previous studies and those resulting from this work, it would be useful to
present together the values obtained in both cases.

  > RESPONSE: We now mention the name "BATMAN". We do the same with
  > "emcee".
  >
  > We did not explicitly describe our choice for the initial
  > parameters, because the converged best-fit values from the chain
  > do not depend on them.  For reproducibility purposes, similar
  > best-fit values can be obtained independent of initial parameter
  > choices. Barring an overruling request from the referee, we will
  > not mention our explicit choice in the text (it was to use values
  > from Hoyer et al., 2013).
  >
  > The transit parameters from the phase-folded fit: Rp/Rstar,
  > inclination, a/Rstar, and limb darkening parameters are given in
  > the first five lines of Table 1.
  >
  > The transit mid-times from the independent fits to each transit
  > are given in Table 2.
  >
  > The parameters which are not reported are the depths of the
  > individual transits, and the linear fit parameters. Since the
  > focus of this study is the transit times, we omitted these
  > additional parameters for the sake of concision.
  >
  > Regarding the suggestion to add a table comparing our
  > stellar/planet parameters with those found by other investigators:
  > again, because the focus of the paper is the transit times, we
  > have left the interested reader to explore these differences by
  > pointing them to the relevant studies in the last paragraph of
  > Section 2.3. From e.g., Table 8 of Southworth+2009, we see that
  > our values do agree with those of previous studies, and so do not
  > merit further attention, given the main focus of the present work.

REFEREE COMMENT

@@

  > So yes, we used the same transit model as before (the BATMAN
  > code), but with the addition of the slope and intercept of a
  > linear trend as free parameters.  Our proceduring for
  > determining the mid-transit time uncertainties is also
  > described.

REFEREE COMMENT

v) Is χ^2=9.2 the reduced chi-square? If it is so, It should be clarified by
using a different symbol or by adding a sub-index, for example. Please, fix
this in the rest of the manuscript when necessary.

  > RESPONSE: $\chi^2 = 9.2$ is the $\chi^2$ value. We have
  > corrected the typo in the text, in which we wrote "reduced
  > $\chi^2$", which likely led to the confusion!

REFEREE COMMENT

@@

  > RESPONSE: Done.

REFEREE COMMENT

iii) It would be important to introduce references for equations (4) and (5).
Also, for the casual reader, It might be informative to give a brief
explanation of what sidereal and anomalistic periods are.

  > RESPONSE: Equations (4) and (5) are generic equations for the
  > Taylor series expansion of the transit and occultation times as a
  > function of epoch, and so do not require references.  We have
  > added the following sentence to describe the sidereal and
  > anomalistic periods: "The sidereal period is the duration required
  > to return to the same orientation with respect to the stars; the
  > slightly longer anomalistic period is the duration required to
  > reach a fixed longitude with respect to the rotating line of
  > apsides."

REFEREE COMMENT

@@

  > RESPONSE: Done.

REFEREE COMMENT

v) Similar to i) How did you fit the mid-transit times and occultations shown
in Figure 4?

  > RESPONSE: We have added the following sentences in Section 3.2:
  > "We fit each model by assuming a Gaussian likelihood and sampling
  > over the posterior probability distributions. The prior for the
  > quadratic model allowed the period derivative to have any sign."
  > We have clarified the wording throughout from "decreasing-period
  > model" to "quadratic model" to reflect the latter point.

REFEREE COMMENT

@@

  > RESPONSE: The caption now reads "Best-fit transit timing model
  > parameters".

REFEREE COMMENT

vii) Given that the mid-transit times values used in this work are taken from
different authors with different methodologies to perform the fitting and
detrending of the light curves, could the authors mention how this could affect
their results?

  > RESPONSE: We have added the following paragraph at the end of
  > Section 3.3:

  > There is a final systematic concern in our global methodology.  We
  > have opted to use mid-transit time values derived by different
  > authors, who used heterogeneous methods to fit and detrend their
  > lightcurves.  One important assumption is of course that these authors
  > have correctly documented their time systems.  Further, though many
  > assumptions in transit-fitting ({\it e.g.}, concering limb-darkening
  > and eccentricity) do not affect transit-time measurements, different
  > detrending approaches can asymmetrically warp transits and shift
  > mid-transit times.  The magnitude of this systematic effect is hard to
  > quantify, but the situation is fairly clear from
  > Figure~\ref{fig:times}.  Many independent authors provided transit
  > measurements shortly after WASP-4b's discovery, so the data should on
  > average be acceptable.  \citet{huitson_gemini_2017} provided the most
  > important data from epochs 0-1000, and so if their data were
  > systematically affected by detrending choices at the level of many
  > times their reported uncertainties, our reported timing anomaly would
  > be suspect.  For this reason, we have paid extra attention to the
  > \citet{huitson_gemini_2017} data set, corresponding with the authors
  > to confirm that such systematic concerns would not affect their
  > results at the many-$\sigma$ level.

REFEREE COMMENT

4. INTERPRETATION

@@

REFEREE COMMENT:

ii) In the caption of Figure 7: "with standard deviation (σpredicted)" -->
"with standard deviation (σpre-TESS)"

  > RESPONSE: Corrected.

********************************************************************************
OTHER CHANGES:

@@

* Added the following coauthors: Fei Dai, Natalia Guerrero, Bill Wohler,
  Douglas Caldwell.

* Minor edits in text throughout, as indicated with the \added{},
  \deleted{}, and \replaced{}{} commands.

* Minor tweaks to figures.

### 2019-03-06 paper/ms.tex
Update ms.tex

Although the Transiting Exoplanet Survey Satellite (TESS\added{,
\citealt{ricker_transiting_2015}}) is designed to detect new planets,
it is also \replaced{performing precise photometric monitoring
of}{precisely monitoring} most of the planets that have been
discovered by ground-based transit surveys over the last two decades.
One \replaced{of the applications}{application} of the new TESS data
is to search for timing anomalies in \added{previously known }hot
Jupiter systems.  Long-term monitoring of hot Jupiter transit and
occultation times should eventually reveal \replaced{two
distinct}{three select} processes.

@@

First, the orbits of most hot Jupiters should shrink because of tidal
orbital decay
\citep{counselman_outcomes_1973,hut_stability_1980,levrard_falling_2009,matsumura_tidal_2010}.
Directly measuring the rate of decay might lead to an improved
understanding of how friction dissipates the energy of tidal
disturbances (a problem reviewed by \citealt{Mazeh2008} and
\citealt{ogilvie_tidal_2014}).

Second, if hot Jupiter orbits are at all eccentric, then long-term
timing studies should reveal rotation of the orbital ellipse within
the orbital plane (``apsidal precession'').  If this effect were
observed, it could yield a measure of the planet's Love number, which
would constrain the planet's interior structure
\citep{ragozzine_probing_2009}.

The most convincing direct evidence yet found for either orbital decay
or apsidal precession of a hot Jupiter is the case of WASP-12b, which
has a transit period that has decreased by about 30~milliseconds per
year over the last decade
\citep{maciejewski_departure_2016,patra_2017}.

@@

Here, we present evidence for a timing anomaly in the WASP-4 system.
The hot Jupiter WASP-4b orbits a G7V star every 1.34 days,
corresponding to an orbital distance of 5.5 stellar radii
\citep{wilson_wasp-4b_2008,huitson_gemini_2017}.  It is a good target
to search for departures from a constant period, because transit data
exist all the way back to 2007.  The orbital eccentricity is less than
0.018 (2$\sigma$), based on the work of \cite{knutson_friends_2014},
who combined the available transit times, occultation times, and
Doppler data.  The sky projection of the stellar obliquity is also
compatible with zero, within about 10 degrees
\citep{triaud_spin-orbit_2010,sanchis-ojeda_starspots_2011}.

In what follows, \S~\ref{sec:observations} presents the new TESS
observations, and \S~\ref{sec:timing} describes our timing analysis.
We tried fitting the data with three models: a constant period, a
decaying period, and a slightly eccentric precessing orbit.  A
constant period can be ruled out\replaced{, but we}{. We} cannot
distinguish between the \replaced{latter two possibilities}{
  possibilities of a decaying orbit, a precessing orbit, and the
  unmodeled possibility of an orbit being gravitationally perturbed by
  an outer companion}.  \replaced{Either possibility}{Any of the three
scenarios} would have interesting implications\replaced{, described in
\S~\ref{sec:implications}}{ (\S~\ref{sec:implications}), and more data
are required for a definitive ruling (\S~\ref{sec:future}).}
Appendix~\ref{sec:verify_tess} considers the possibility that the
WASP-4 timing anomaly is due to an error in timestamps in the TESS
data products.  We found this possibility to be unlikely because none
of the other hot Jupiters we examined show a timing offset with the
same amplitude as was seen for WASP-4.

@@

WASP-4 was observed by TESS with Camera 2 from August 23 to September
20, 2018, within the second ``sector'' of science operations.  The
star is designated as TIC 402026209 in the TESS Input Catalog
\citep{stassun_TIC_2018}.  The pixel data for an $11\times11$ array
surrounding WASP-4 were averaged into 2-minute stacks by the onboard
computer.  The data were downlinked via the Deep Space Network, and
the spacecraft timestamps were calibrated against the ground-station
clocks.  The spacecraft clock times were then transformed by the
Payload Operations Center into the {\it Temps Dynamique Barycentrique}
(TDB) reference system.  The images were then reduced to lightcurves
by the Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  During this processing, the SPOC used
the known spacecraft trajectory to compute the barycentric time
corrections on a target by target basis, and expressed the timestamps
as Barycentric TESS Julian Dates (BTJD), which is simply the
\replaced{b}{B}arycentric Julian \replaced{d}{D}ate minus
2{,}457{,}000.  Lightcurves that were flagged \deleted{as Threshold
Crossing Events} by the SPOC pipeline \added{as crossing a transit
detection threshold} were then vetted and released by the MIT TESS
Science Office to the Mikulski Archive for Space Telescopes on
November 29, 2018~\citep{ricker_tess_alerts_2018}.

@@

All told, we removed 8\% of the original data points, and were left
with 18{,}165 measurements of the relative flux of WASP-4.  We
normalized the data by dividing out the median flux.  We converted the
timestamps from BTJD$_{\rm TDB}$ into BJD$_{\rm TDB}$ by adding the
appropriate 2457000 day offset
\citep{tess_data_product_description_2018}.  Many of these and
subsequent processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018}. We did not
``flatten'' the lightcurves, as is often done with splines,
polynomials, or Gaussian processes.  Instead, we modeled the
out-of-transit flux variations simultaneously with the transit
parameters, as described below.

@@

Figure~\ref{fig:lightcurves} shows the lightcurve of each individual
transit, the best-fit models, and the residuals.  Table~2 reports the
mid-transit times and their uncertainties.  After binning the
residuals to 1-hour windows, the lightcurves have an rms scatter of
586\,{\rm ppm}.  The pre-launch TESS noise
model\footnote{\url{github.com/lgbouma/tnm}}
(\citealt{winn_photonflux_2013}, \citealt{Sullivan_2015} Section 6.4)
would have predicted an error budget consisting of the following terms
added in quadrature: 410\,{\rm ppm} from photon-counting noise,
202\,{\rm ppm} from detector read noise, and 673\,{\rm ppm} from the
zodiacal background light.  The level of background light appears to
have been overestimated.

@@

\explain{The following subsection has been added since the original
submission, per the referee's suggestions.}
\subsection{Systematic concerns}

\paragraph{Omitting suspect pre-TESS transits}
To assess the robustness of these results, we considered a few
possible systematic effects in the timing dataset.  One concern in the
pre-TESS measurements was incomplete phase coverage: a handful
of the transit times in Table~2 are from lightcurves with partial
gaps.  A separate issue is the effect of spot-crossing anomalies on
mid-transit time measurements.  To address these concerns, we repeated
the model-fitting described above, but omitted epochs -827, -804,
-537, and -208 because of gaps in their coverage.  We also omitted
epochs -526 and -561 because of visible spot anomalies during the
transits. (All epoch numbers are as in Table~2.)  The resulting
best-fit transit timing model parameters were all within $1\sigma$ of
the values quoted in Table~4.  The uncertainties, goodness-of-fit
statistics, and model comparison statistics did not appreciably
change.

\paragraph{Spot-crossing events in TESS data}
To explore the effect of possible spot-crossing events on the TESS
transit time measurements, we performed a separate test.  We injected
triangular spot-anomalies with amplitude $0.03\%$ and duration 30
minutes at random phases into each transit.  The amplitudes were
larger than the spot-crossing anomalies observed by
\citet{southworth_high-precision_2009} and
\citet{sanchis-ojeda_starspots_2011}, and the durations were
comparable.  Spots of these amplitudes resemble the anomalies present
in transits ``1360.54'' and ``1372.58'' of Figure
\ref{fig:lightcurves}: they are visible, but at low confidence.

With spots injected, we repeated our measurement of the transit times.
On average, the measured transit times did not change with spots
injected, because the flux deviations are symmetric about the transit
minimum.  For individual transits, there were no cases for which the
timing deviation was larger than one minute.  The most concerning
shift occurs when the spot anomaly occurs during transit egress, in
which case the measured mid-time is shifted early by between 30 and 50
seconds \citep[qualitatively similar to results found
by][]{ioannidis_how_2016}.

@@

\paragraph{Detrending choices in pre-TESS data}
There is a final systematic concern in our global methodology.  We
have opted to use mid-transit time values derived by different
authors, who used heterogeneous methods to fit and detrend their
lightcurves.  This of course assumes that these authors
have correctly documented their time systems.  Further, though many
choices in transit-fitting ({\it e.g.}, parametrization of
limb-darkening and eccentricity) do not affect transit mid-time
measurements, different detrending approaches can asymmetrically warp
transits and shift mid-transit times.  The magnitude of this
systematic effect is hard to quantify, but the situation is fairly
clear from Figure~\ref{fig:times}.  Many independent authors provided
transit measurements shortly after WASP-4b's discovery, so the data
should on average be acceptable.  \citet{huitson_gemini_2017} provided
the most important data from epochs 0-1000, and so if their data were
systematically affected by detrending choices at the level of many
times their reported uncertainties, our timing anomaly would
be suspect.  For this reason, we paid careful attention to the
\citet{huitson_gemini_2017} data set, and corresponded with the authors
to confirm that their results are not affected by systematic 
effects of the required amplitude.

None of the concerns mentioned in this subsection are likely
explanations for the observed timing variations. We proceed by
considering possible astrophysical explanations.

@@

If the timing variation is \deleted{being caused }caused entirely by
orbital decay, then \replaced{the}{the best-fit model parameters yield a}
characteristic\replaced{ timescale of the decay is}{ decay timescale of}
\begin{equation}
  \frac{P}{ \dot{P} } = 9.2 \, {\rm Myr}.
\end{equation}
For comparison, the corresponding time for WASP-12b is 3.2\,Myr
\citep{patra_2017}.

>>>>

Although the Transiting Exoplanet Survey Satellite (TESS\added{,
\citealt{ricker_transiting_2015}}) is designed to detect new planets,
it is also \replaced{performing precise photometric monitoring
of}{precisely monitoring} most of the planets that have been
discovered by ground-based transit surveys over the last two decades.
One \replaced{of the applications}{application} of the new TESS data
is to search for timing anomalies in \added{previously known }hot
Jupiter systems.  Long-term monitoring of hot Jupiter transit and
occultation times should eventually reveal \replaced{two
distinct}{variations caused by three different} \replaced{processes}{phenomena}.

@@

First, the orbits of most hot Jupiters should shrink because of tidal
orbital decay
\citep{counselman_outcomes_1973,hut_stability_1980,levrard_falling_2009,matsumura_tidal_2010}.
Directly measuring the rate of decay might lead to an improved
understanding of how friction dissipates the energy of tidal
disturbances (a problem reviewed by \citealt{Mazeh2008} and
\citealt{ogilvie_tidal_2014}). Second, if hot Jupiter orbits are appreciably eccentric, then long-term
timing studies should reveal rotation of the orbital ellipse within
the orbital plane (``apsidal precession'').  If this effect were
observed, it could yield a measure of the planet's Love number, which
would constrain the planet's interior structure
\citep{ragozzine_probing_2009}.
The most convincing direct evidence yet found for either orbital decay
or apsidal precession of a hot Jupiter is the case of WASP-12b, which
has a transit period that has decreased by about 30~milliseconds per
year over the last decade
\citep{maciejewski_departure_2016,patra_2017}.

@@

Here, we present evidence for a timing anomaly in the WASP-4 system.
The hot Jupiter WASP-4b orbits a G7V star every 1.34 days,
corresponding to an orbital distance of 5.5 stellar radii
\citep{wilson_wasp-4b_2008,huitson_gemini_2017}.  It is a good target
to search for departures from a constant period, because transits
have been observed since 2007.  The orbital eccentricity is less than
0.018 (2$\sigma$), based on the work of \cite{knutson_friends_2014},
who combined the available transit times, occultation times, and
Doppler data.  The sky projection of the stellar obliquity is also
compatible with zero, within about 10 degrees
\citep{triaud_spin-orbit_2010,sanchis-ojeda_starspots_2011}.

In what follows, \S~\ref{sec:observations} presents the new TESS
observations, and \S~\ref{sec:timing} describes our timing analysis.
We tried fitting the data with three models: a constant period; a
steadily shrinking period; and a slightly eccentric, precessing orbit.  A
constant period can be ruled out\replaced{, but we}{. We} cannot
distinguish between the \replaced{latter two possibilities}{
  possibilities of a decaying orbit, a precessing orbit, and the
  unmodeled possibility of an orbit being gravitationally perturbed by
  an outer companion}.  \replaced{Either possibility}{Any of the three
scenarios} would have interesting implications\replaced{, described in
\S~\ref{sec:implications}}{ (\S~\ref{sec:implications}), and more data
are required for a definitive ruling (\S~\ref{sec:future}).}
Appendix~\ref{sec:verify_tess} considers the possibility that the
WASP-4 timing anomaly is due to an error in timestamps in the TESS
data products.  We found this possibility to be unlikely because none
of the other hot Jupiters we examined show a timing offset with the
same amplitude as was seen for WASP-4.

@@

WASP-4 was observed by TESS with Camera 2 from August 23 to September
20, 2018, within the second ``sector'' of science operations.  The
star is designated as TIC 402026209 in the TESS Input Catalog
\citep{stassun_TIC_2018}.  The pixel data for an $11\times11$ array
surrounding WASP-4 were averaged into 2-minute stacks by the onboard
computer.  The data were downlinked via the Deep Space Network\footnote{\url{https://deepspace.jpl.nasa.gov}}, and
the spacecraft timestamps were calibrated against the ground-station
clocks.  The spacecraft clock times were then transformed by the
Payload Operations Center into the {\it Temps Dynamique Barycentrique}
(TDB) reference system.  The images were then reduced to lightcurves
by the Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  During this processing, the SPOC used
the known spacecraft trajectory to compute the barycentric time
corrections on a target by target basis, and expressed the timestamps
as Barycentric TESS Julian Dates (BTJD), which is simply the
\replaced{b}{B}arycentric Julian \replaced{d}{D}ate minus
2{,}457{,}000.  Lightcurves that were flagged \deleted{as Threshold
Crossing Events} by the SPOC pipeline \added{as crossing a transit
detection threshold} were then vetted and released by the MIT TESS
Science Office to the Mikulski Archive for Space Telescopes on
November 29, 2018~\citep{ricker_tess_alerts_2018}.

@@

All told, we removed 8\% of the original data points, and were left
with 18{,}165 measurements of the relative flux of WASP-4.  We
normalized the data by dividing out the median flux.  We converted the
timestamps from BTJD$_{\rm TDB}$ into BJD$_{\rm TDB}$ by adding the
appropriate 2{,}457{,}000 day offset
\citep{tess_data_product_description_2018}.  Many of these and
subsequent processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018}. We did not
``flatten'' the lightcurves, as is often done with splines,
polynomials, or Gaussian processes.  Instead, we modeled the
out-of-transit flux variations simultaneously with the transit
parameters, as described below.

@@

Figure~\ref{fig:lightcurves} shows the lightcurve of each individual
transit, the best-fit models, and the residuals.  Table~2 reports the
mid-transit times and their uncertainties.  After binning the
residuals to 1-hour windows, the lightcurves have an rms scatter of
586\,{\rm ppm}.  The pre-launch TESS noise
model\footnote{\url{github.com/lgbouma/tnm}}
(\citealt{winn_photonflux_2013}, \citealt{Sullivan_2015} Section 6.4)
would have predicted an error budget consisting of the following terms
added in quadrature: 410\,{\rm ppm} from photon-counting noise,
202\,{\rm ppm} from detector read noise, and 673\,{\rm ppm} from the
zodiacal background light.  The level of background light appears to
have been overestimated in the model.

@@

\explain{The following subsection has been added since the original
submission, per the referee's suggestions.}
\subsection{Possible systematic errors}

To assess the robustness of these results, we considered a few
possible systematic effects in the timing dataset.

\paragraph{Suspect pre-TESS light curves}
Some of the
pre-TESS light curves have incomplete phase coverage: a handful
of the transit times in Table~2 are from lightcurves with 
gaps.  A separate issue is the effect of spot-crossing anomalies on
transit timings.  To address these concerns, we repeated
the model-fitting described above, but omitted epochs -827, -804,
-537, and -208 because of gaps in their coverage.  We also omitted
epochs -526 and -561 because of visible spot anomalies during the
transits. (All epoch numbers are as in Table~2.)  The resulting
best-fit transit timing model parameters were all within $1\sigma$ of
the values quoted in Table~4.  The uncertainties, goodness-of-fit
statistics, and model comparison statistics did not appreciably
change.

\paragraph{Spot-crossing events in TESS data}
To explore the effect of possible spot-crossing events on the TESS
transit time measurements, we performed a separate test.  We injected
triangular spot-anomalies with amplitude $0.03\%$ and duration 30
minutes at random phases into each transit.  The amplitude was
chosen to be larger than the spot-crossing anomalies observed by
\citet{southworth_high-precision_2009} and
\citet{sanchis-ojeda_starspots_2011}, and the duration was chosen
to be comparable to those of previously observed events.
Spots of these amplitudes resemble the possible anomalies present
in transits ``1360.54'' and ``1372.58'' of Figure
\ref{fig:lightcurves}.

With spots injected, we repeated our measurement of the transit times.
On average, the measured transit times did not change after injecting spots,
because the flux deviations are equally likely to occur
in the first and second halves of the transit. 
For individual transits, there were no cases for which the
timing deviation was larger than one minute.  The largest 
shifts occur when the spot anomaly occurs during transit ingress or egress, in
which case the measured mid-time is shifted early by between 30 and 50
seconds \citep[qualitatively similar to results found
by][]{ioannidis_how_2016}.

@@

\paragraph{Detrending choices in pre-TESS data}
There is a final concern that is difficult to address.  We
collected the mid-transit time values derived by different
authors, who used heterogeneous methods to fit and detrend their
lightcurves.  We have also assumed that these authors
have correctly documented the time systems in which the data are
reported.  Further, though many
choices in transit-fitting ({\it e.g.}, parametrization of
limb-darkening and eccentricity) do not affect transit mid-time
measurements, different detrending approaches can asymmetrically warp
transits and shift mid-transit times.  The magnitude of this
systematic effect is hard to quantify, but the situation is fairly
clear from Figure~\ref{fig:times}.  Many independent authors provided
transit measurements shortly after WASP-4b's discovery, and the data are
consistent with each other. \citet{huitson_gemini_2017} provided
the most important data from epochs 0-1000. If their data were
systematically affected by detrending choices or time-system confusion
at the level of several
times their reported uncertainties, then it possible that the orbital
period is constant despite the evidence in the TESS data.
For this reason, we paid careful attention to the
\citet{huitson_gemini_2017} data set, and corresponded with the authors
to confirm that their results are not affected by systematic 
effects of the required amplitude.

None of the concerns mentioned in this subsection seem likely
to explain the observed timing variations. We proceed by
considering possible astrophysical explanations.

@@

If the timing variation is \deleted{being caused }caused entirely by
orbital decay, then \replaced{the}{the best-fit model parameters yield a}
characteristic\replaced{ timescale of the decay is}{ decay timescale of}
\begin{equation}
  \frac{P}{ {\rm d}P/{\rm d}t } = 9.2 \, {\rm Myr}.
\end{equation}
For comparison, the corresponding time for WASP-12b is 3.2\,Myr
\citep{patra_2017}.
